Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
pdf update

Arizona remains a pivotal swing state, particularly given its recent shifts in party alignment in the past two elections. In 2016, Trump won Arizona with 49% of the vote to Clinton's 45.5%, a relatively substantial margin for a swing state. However, in 2020, Biden narrowly won with 49.4% to Trump’s 49.1%, highlighting Arizona's competitiveness for the 2024 election, which is what makes Arizona such an important state.
As seen in @fig-supportAM, Harris's polling numbers were initially around 42%, but have significantly increased in the most recent polls. Despite this trend, @fig-supportstate indicates that Trump still has larger support in the state, with Arizona having the largest polling difference in his favor among the swing states (@towin270).

@@

Nevada is a state who's majority is dessert and wilderness, with two large cities being Reno and Las Vegas, as the case is with many states a Majority of democratic votes come from large cities and the majority of republican votes coming from rural areas. Nevada has been a democratic state for the last 4 elections with at least a 2% difference in favor of the democrats in the last two elections @towin270.

>>>>

Arizona is a very important swing state especially as the state has switches which party they voted for in in the last two elections with Trump winning 49% of the vote and Clinton with 45.5%, which considering Arizona is a swing state is a rather significant6 margin. While in the 2020 election Biden ended up winning Arizona with 49.4% of the vote and Trump 49.1%, which is a much smaller margin of victory and what makes Arizona so questionable in the 2024 election.

We can see in @fig-supportAM that while the polling numbers for Harris started somewhat low around 42%, the have gone up significantly and have continued to trend upwards in the most recent polls. Although, in the @fig-supportstate trump still has larger support in the state, and the largest polling difference in Trump's favour out of all the swing states polled (@towin270).

@@

Nevada, primarily composed of desert and rural areas, sees its Democratic support concentrated in urban centers like Reno and Las Vegas compared to rural areas. The state has voted Democratic in the last four elections, with a 2% or greater margin in favor of Democratic candidates in the past two.
Nevada has been a democratic state for the last 4 elections with at least a 2% difference in favor of the democrats in the last two elections @towin270.
